---
title: "Exploratory Analysis"
author: "Eva Jason"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(dplyr)
library(ggplot2)
library(tidyr)
library(kableExtra)
```

```{r}
df_all <- read.csv("../HPS_Week17_PUF_CSV/pulse2020_puf_17.csv") 
```

```{r}
df <- mutate(df_all, age = 2023-TBIRTH_YEAR) %>%
  mutate(ANXIOUS = ifelse(ANXIOUS < 1, 0, ANXIOUS)) %>%
  mutate(WORRY = ifelse(WORRY < 1, 0, WORRY)) %>%
  mutate(INTEREST = ifelse(INTEREST < 1, 0, INTEREST)) %>%
  mutate(DOWN = ifelse(DOWN < 1, 0, DOWN)) %>%
  mutate(mental_health_score = rowSums(pick(ANXIOUS,WORRY,INTEREST,DOWN))) %>%
  mutate(issue = ifelse(mental_health_score<=4, 0, 1)) %>%
  mutate(age_group = case_when(
    age < 30 ~ "20-29",
    age < 40 & age >29 ~ "30-39",
    age < 50 & age >39 ~ "40-49",
    age < 60 & age > 49 ~ "50-59",
    age < 70 & age >59 ~ "60-69",
    age < 80 & age >69 ~ "70-79",
    age > 79 ~ "80+"
  ))
```

## Summary Statistics

```{r}
ggplot(df, aes(age)) +
  geom_bar() +
  theme_minimal()

avg_age <- mean(df$age)
median_age <- median(df$age)
```

A total of `r nrow(df)` responded to the Week 17 surrvey. The average age of respondents was `r round(avg_age,2)` and the median age was  `r round(median_age,2)`.

```{r}
df_mental_health <- select(df, ANXIOUS, WORRY, INTEREST, DOWN, age) %>%
  pivot_longer(cols = c(ANXIOUS,WORRY,INTEREST,DOWN), names_to ="issue", values_to = "score") %>%
  mutate(age_group = case_when(
    age < 30 ~ "20-29",
    age < 40 & age > 29 ~ "30-39",
    age < 50 & age > 39 ~ "40-49",
    age < 60 & age > 49 ~ "50-59",
    age < 70 & age > 59 ~ "60-69",
    age < 80 & age > 69 ~ "70-79",
    age > 79 ~ "80+"
  ))

df_groups <- group_by(df_mental_health, issue, age_group, score) %>%
  summarise(total_issue_age_score = n())

df_groups_age_group_total_score <-  group_by(df_mental_health, age_group, issue) %>%
  summarise(total_issue_age = n())

df_groups <- merge(df_groups, df_groups_age_group_total_score) %>%
  mutate(percent = total_issue_age_score/total_issue_age)

ggplot(df_groups, aes(x=score, y = percent)) +
  geom_col() +
  facet_grid(issue~age_group) +
  theme_minimal()
```

"Over the last 7 days, how often have you been bothered by the following problems ... Feeling
nervous, anxious, or on edge? Would you say not at all, several days, more than
half the days, or nearly every day? Select only one answer."

"1) Not at all
2) Several days
3) More than half the days
4) Nearly every day 
-99) Question seen but category not selected
-88) Missing / Did not report"


"Over the last 7 days, how often have you been bothered by the following problems ... Not being
able to stop or control worrying? Would you say not at all, several days, more
than half the days, or nearly every day? Select only one answer."
"1) Not at all
2) Several days
3) More than half the days
4) Nearly every day 
-99) Question seen but category not selected
-88) Missing / Did not report"


"Over the last 7 days, how often have you been bothered by ... having little interest or
pleasure in doing things? Would you say not at all, several days, more than
half the days, or nearly every day? Select only one answer."
"1) Not at all
2) Several days
3) More than half the days
4) Nearly every day 
-99) Question seen but category not selected
-88) Missing / Did not report"


"Over the last 7 days, how often have you been bothered by ... feeling down, depressed, or
hopeless? Would you say not at all, several days, more than half the days, or
nearly every day? Select only one answer."

1) Not at all
2) Several days
3) More than half the days
4) Nearly every day 
-99) Question seen but category not selected
-88) Missing / Did not report"


```{r}
df_groups_y_n_issue <- group_by(df, issue, age_group) %>%
  summarise(total_issue_age_score = n())

df_groups_age_group <-  group_by(df, age_group) %>%
  summarise(total_age_group = n())

df_groups <- merge(df_groups_y_n_issue, df_groups_age_group) %>%
  mutate(percent = total_issue_age_score/total_age_group)%>%
  mutate(has_issue = ifelse(issue ==1, "YES", "NO"))

ggplot(df_groups, aes(x=age_group, y = percent, fill = has_issue)) +
  geom_col(position="dodge") +
  theme_minimal()
```

```{r}
mod.fit <- glm(formula = issue ~ age, family = binomial(link = logit), data = df)

agg.age <- aggregate(x = issue ~ age, data= df, FUN = sum)
agg.age  <- cbind(agg.age, aggregate(x = issue ~ age,data= df, FUN = length))
names(agg.age)[4] <- 'total'

mod.fit2 <- glm(formula = issue/total ~ age,family = binomial(link='logit'), data = agg.age, weight = total)

curve(predict(mod.fit2, data.frame(age=x), type="response"),from=min(agg.age$age), to=max(agg.age$age), ylab="Probability", xlab="Age")
```
```{r}
df_activity <- select(df,FEWRTRANS,PLNDTRIPS,CNCLDTRPS,TW_START,CHNGHOW1,CHNGHOW2,CHNGHOW3,CHNGHOW4,CHNGHOW5,CHNGHOW6,CHNGHOW7,CHNGHOW8,CHNGHOW9,CHNGHOW10,CHNGHOW11,CHNGHOW12)
  
df_change <- select(df, starts_with("CHNGHOW"))

df_change[df_change == -99] <- 0
df_change[df_change == -88] <- 0

df_total_change <- colSums(df_change)

df_change <- data.frame(category = colnames(df_change), total =colSums(df_change)) %>%
  mutate(total = as.numeric(total)) %>%
  mutate(percentage = total/nrow(df_change)) %>%
  mutate(percent = paste0(round(percentage, 2)*100, "%"))

kable(select(df_change, category, percent), row.names = F)
```


How did spending or shopping change	In the last 7 days, which of the following changes have you or your household made to your spending or shopping? Select all that apply. 
"1) Made more purchases online (as opposed to in store)
-99) Question seen but category not selected
-88) Missing / Did not report"	
All persons born before 2002	
	
How did spending or shopping change	In the last 7 days, which of the following changes have you or your household made to your spending or shopping? Select all that apply. 
"1) Made more purchases by curbside pick-up (as opposed to in store)
-99) Question seen but category not selected
-88) Missing / Did not report"	
All persons born before 2002	
	
How did spending or shopping change	In the last 7 days, which of the following changes have you or your household made to your spending or shopping? Select all that apply. 
"1) More purchases in-store (as opposed to purchases online or curbside pickup)
-99) Question seen but category not selected
-88) Missing / Did not report"	
All persons born before 2002	
	
How did spending or shopping change	In the last 7 days, which of the following changes have you or your household made to your spending or shopping? Select all that apply. 
"1) Increased use of credit cards or smartphone apps for purchases, instead of using cash 
-99) Question seen but category not selected
-88) Missing / Did not report"	
All persons born before 2002	
	
How did spending or shopping change	In the last 7 days, which of the following changes have you or your household made to your spending or shopping? Select all that apply. 
"1) Increased use of cash instead of using credit cards or smartphone apps for purchases
-99) Question seen but category not selected
-88) Missing / Did not report"	
All persons born before 2002	
	
How did spending or shopping change	In the last 7 days, which of the following changes have you or your household made to your spending or shopping? Select all that apply. 
"1) Avoided eating at restaurants
-99) Question seen but category not selected
-88) Missing / Did not report"	
All persons born before 2002	
	
How did spending or shopping change	In the last 7 days, which of the following changes have you or your household made to your spending or shopping? Select all that apply. 
"1) Resumed eating at restaurants
-99) Question seen but category not selected
-88) Missing / Did not report"	
All persons born before 2002	
	
How did spending or shopping change	In the last 7 days, which of the following changes have you or your household made to your spending or shopping? Select all that apply. 
"1) Canceled or postponed in-person medical or dental appointments 
-99) Question seen but category not selected
-88) Missing / Did not report"	
All persons born before 2002	
	
How did spending or shopping change	In the last 7 days, which of the following changes have you or your household made to your spending or shopping? Select all that apply. 
"1) Attended in-person medical or dental appointments
-99) Question seen but category not selected
-88) Missing / Did not report"	
All persons born before 2002	
	
How did spending or shopping change	In the last 7 days, which of the following changes have you or your household made to your spending or shopping? Select all that apply. 
"1) Canceled or postponed housekeeping or caregiving services
-99) Question seen but category not selected
-88) Missing / Did not report"	
All persons born before 2002	
	
How did spending or shopping change	In the last 7 days, which of the following changes have you or your household made to your spending or shopping? Select all that apply. 
"1) Resumed or started new housekeeping or caregiving services 
-99) Question seen but category not selected
-88) Missing / Did not report"	
All persons born before 2002	
	
How did spending or shopping change	In the last 7 days, which of the following changes have you or your household made to your spending or shopping? Select all that apply. 
"1) Did not make any changes to spending or shopping behavior
-99) Question seen but category not selected
-88) Missing / Did not report"	
All persons born before 2002	
	
